---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Lex2Emo

<!-- badges: start -->
<!-- badges: end -->

## Installation

You can install the current version of Lex2Emo using devtools:
```{r, echo=FALSE}
devtools::install_github("https://github.com/Reilly-ConceptsCognitionLab/Lex2Emo.git")
```

## Reading in a directory of .txt files

Emo2Lex provides a method (readText) that allows users to concatonate a directory of .txt files into a single data frame meeting the format requirements for the next stage.
Each file is read in as a single string of text, with only newlines removed, however non-alphanumeric characters are removed in the next stage.

## Requirements for dataframe input

Data frame inputs must at the least contain a column with text data called 'Text' and an ID column (called 'ID') used to differentiate each text sample. Currently, an ID column is required even if a single text sample is provided.
Lex2Emo will treat any data outside of the 'Text' and 'ID' columns as metadata and preserve the first entry for each document ID when aggregated.

### Basic example of data frame for input into transformText()

```{r, echo=FALSE}
text <- c("A description of something", 
          "The entirety of a book", 
          "A whole conversation")
exampleData <- data.frame(ID = 1:length(text),
                          Text = text,
                       Length = c(55, 80000, 700))
knitr::kable(exampleData)
```


## Using transformText()

transformText() transforms each word in each text sample into it's associated ratings (if available) on 22 emotional dimensions.

```{r}
library(Lex2Emo)
# example of transformText() calls to output aggregated data
aggTextData <- transformText(textData = exampleData, returnFullData = F)

# example of transformText() calls to output non-aggregated data
aggTextData <- transformText(textData = exampleData, returnFullData = T)
```




